An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-30 EconGrowth2.Rnw
typo fix

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType="none", facet_formula= ~countryAbbrev )
@

@@

<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q", facet_formala=~countryAbbrev)
@

>>>>

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
@

@@

<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
@
